% Permission is granted to copy, distribute and/or modify this document
% under the terms of the GNU Free Documentation License, Version 1.3
% or any later version published by the Free Software Foundation;
% with no Invariant Sections, no Front-Cover Texts, and no Back-Cover Texts.
% A copy of the license is included in the section entitled "GNU
% Free Documentation License".
%
% Authors:
% Caner Candan <caner@candan.fr>, http://caner.candan.fr

\begin{document}

\pagestyle{empty}

\noindent
{\Large \textsc{Geraldine Starke}}

\noindent
\begin{flushright}
  \smallskip
  \lang{birth date: 1$^{st}$ june 1987}{date de naissance: 1 juin 1987}{Geburtsdatum : 1. Juni 1987}
  \hfill
  \lang{phone: +33.}{télephone: 0}{Telefon: +33.}647782400\\
  \lang{citizenship: french, german}{citoyenneté: française, allemande}{Staatsbürgerschaft : französich, deutsch}
  \hfill
  e-mail: geraldine@starke.fr\\
  \lang{driving license}{permis B}{Führerschein B}
  \hfill
  \url{http://fr.linkedin.com/in/geraldinestarke/}\\
\end{flushright}

\smallskip

\specialisation{\lang{Ethical event manager}{Manager Adjoint}{Eventmanager auf ethischer Grundlage}}

\bigskip

{\bf \lang{Summary}{Résumé}{Zusammenfassung}}: 
\lang{
  Event manager, specialized in green events. Vegan and rawfood expert.
  Multilingual, independent, hospitality back-grounded and with good computer/internet skills, entrepreneur. Professional event manager highly involved in ecology and ethics.

  CEO of a vegan online-shop in France, with a new paradigm of e-commerce based on regular cart subscriptions. Also B to B company, working with several partners. 
}{%
  
}{%
  Eventmanager, spezialisiert auf "grüne" Veranstaltungen. Vegan und Rawfood Expertin.
  Mehrsprachig, unabhängig, basierend auf "Hospitality" und mit guter Computer/Internet Kompetenz, Unternehmer. Professionnelle eventmanagerin mit ausgeprägtem Bezug zu Ökologie und Ethik.

  Geschäftsführerin eines online Vertriebs auf veganer Basis in Frankreich, mit neuer Ausrichtung im e-commerce basierend zur Abonnierung entsprechender Warenkörbe. Auch in Zusammenarbeit mit unterschiedlichen Geschäftspartnern "B to B company". 
}

{\bf \lang{Languages}{Langues}{Sprachen}:}
\lang{
  French (native),
  German (native),
  English (excellent knowledge)
}{%
  Français (langue maternelle),
  Allemand (langue paternelle),
  Anglais (excellent)
}{%
  Französich (Muttersprache)
  Deutsch (Muttersprache)
  English (excellente Kenntnisse) 
}

% Experience
\section{\lang{Experience}{Expériences professionnelles}{Berufserfahrung}}
\begin{CV}[2]{-4.5ex}
  \smallskip

% Juin 2013 - ...
\lang{\item[2013-now]}{\item[2013-aujourd'hui]}{\item[2013-jetzt]}
  \lang{%
    {\bf Event planning consultant,}
    Happy Ending, Angers, France.

    {\it Created my second business : an ethical and ecological oriented event-planning enterprise. Plannification and organization of sustainable, responsible and vegan events. Selecting and transforming venues to accommodate clients’ needs, while respecting the environment.
Manage budgets of up to 30k\euro\ and more.
    Created website from scratch.
    Ergonomic design, web languages, blogging.

    http://happy-ending.org/ }
    
    {\bf Skills :} Budgeting, researching and selecting providers, coordination of the several steps, develop strong relationship with responsible professionals, managing a team of professionnals on the D-day, maintain website and blogging, creative project ideas, high availability and flexibility, good organizational skills (using several organization tools), looking out for the last international event trends.
  }{%
  
  }{%
    {\bf Event  planning consultant,}
    Happy Ending, Angers, Frankreich
     
    {\it Gründung eines zweiten Geschäftszweiges : ein  Unternehmen zur Planung von Verantstaltungen, mit ethischer- und ökologischer Ausgerichtung. Planung und Organisation von nachhaltigen, umweltkompatiblen, veganischen Events. Auswahl und Umgestaltung von örtlichen Gegebenheiten angepasst an die Bedürfnisse der Clientel unter Berücksichtigung des ökologischen Umfelds.
     Durchführung von Verantstalltungen  mit einem Budget ab 30K\euro\ aufwärts 
     Creation einer Website von A bis Z "scratch".
     Ergonomisches Design, Websprachen, blogging
     http://happy-ending.org/ }
     
    {\bf Fähigkeiten} : Budgetierung, Suche und Auswahl der Provider,  Koordination der einzelnen Schritte, Schaffung von gesicherten und zuverlässigen  Geschäftspartnerschaften, Leitung und Abstimmung der diversen  professionnellen Beteiligten auf den Tag "X" hin,  aktualisierung der website und blogging, Ideen für Kreativ-projekte, hohes Anforderungsprofil und Flexibilität, gute Fähigkeiten im Organisationsbereich (unter Ausschöpfung vorhandener Organisationsmittel), ständige Suche nach den letzen internationalen Trends im Eventwesen.
  }

% Mars 2012 - ...
\lang{\item[2012-now]}{\item[2012-aujourd'hui]}{\item[2012-jetzt]}
  \lang{%
    {\bf CEO and Event manager,}
    Vegeclic, Angers, France.

    {\it Started as entrepreneur and created a company named Vegeclic : a vegan online-shop with a new paradigm of e-commerce based on regular cart subscriptions.
    
    Planned and organized several events to represent Vegeclic like fairs, animal welfare events, school presentations or vegan food festivals. 
    Working with several partners in the vegan/ animal welfare world, mostly with organizations, artists, bloggers and professionals. 
    Offered catering services for private household and professionals.

    http://vegeclic.fr/
    
    http://vegeclic.fr/pro }
    
    {\bf Skills :} Budget planning, event manager, stock management (around 1000 products), blog and social network maintaining, new partners and products research, customer service and support.

    
  }{%
  
  }{%
    {\bf Geschäftsführerin und Eventmanagerin}
    Vegeclic, Angers, Frankreich
   
    {\it Start als Unternehmerin durch Creation eines Betriebes mit eingetragenem Firmennamen "Vegeclic" :  ein online-Vertriebs auf veganer Basis, mit neuer  Ausrichtung im e-commerce basierend auf der Môglichkeit zur Abonnierung entsprechender ausgesuchter Warenkörbe.
   
   Bereits durchgeführte Verantstaltungen um "VEGECLIC" vorzustellen unter anderem auf Messen, Tierschutzveranstaltungen, Vorstellung in Schulen, wie auch auf Festivals zur Förderung des Konsums veganisches Lebensmittelprodukte.
   Zusammenarbeit mit verschiedenen Partnern in der veganen- / Tierschutz Welt, vornehmlich mit Organisationen, Künstlern, Bloggern und anderen professionnellen in dem vorgegebenen Bereich.
   Durchführung von Cateringdiensten für private und professionnelle Bezieher.
   
http://vegeclic.fr/
http://vegeclic.fr/pro
  }
    {\bf Fähigkeiten} : Budgetierung, Event plannung und management, Suche und Auswahl an neuen Partners und Produkte, Lagerverwaltung (ungefähr 1000 Produkte), aktualisierung der website und blogging, ständige Suche nach den letzen internationalen Trends im Eventwesen, Kundendienste und support.
}

% Novembre 2010 - ...
\item[2010-2011]
  \lang{%
    {\bf Assistant Manager,}
    Buffalo Grill, Ballainvilliers, France.

    {\it Assistant manager in a well-know chain restaurant.} 
    
      {\bf Skills :} Managing a staff of 30 persons, coordinate the activities of the restaurant and kitchen staff, budgeting and cost controls, inventory management, handle pressure in a highly active enterprise, scheduling staff hours and ordering suppies, staff recruitment, ensure service satisfaction to customers, strong knowledge of Health \& Safety rules and regulations, train new employees, high availability and flexibility.
  }{%
    {\bf Assistant manager,}
    Buffalo Grill, Ballainvilliers, France.
    Manager une équipe. Gérer un service. Gestion administrative du restaurant. Polyvalence.
  }{%
    {\bf Assistant Manager,}
    Buffalo Grill, Ballainvilliers, Frankreich.

    {\it Assistant Manager in einer sehr bekannten Retaurantkette.}

    {\bf Kompetenzen :} Führung einer Mannschaft von 30 Personen, Koordinierung der Aktivitäten des Restaurants und der Küchenequipe,  Budget- und Kostenkontrolle, Inventarmanagement, Umgang mit der besonderen Belastung, wie sie dem hochaktiven Geschäftsumfeld entspricht, Programmierung des Stundenplans der Mitarbeiter und Bestellung der Vorräte, Personnaleinstellung, Qualitätsservicekontrolle / Klientenzufriedenheit, bestes Wissen der Vorschriften und Bestimmungen im Gesundheits- / Sicherheitsbereich, Schulung neuer Mitarbeiter, hohe Disponibilität und Flexibilität.
  }

% September 2009 - Octobre 2010
\item[2009-2010]
  \lang{%
    {\bf Assistant manager}
    Delitraiteur France, Bourg la Reine, France.

    {\it Assistant manager in a luxurious local community store, with a restaurant and catering part. }
    
      {\bf Skills :} Managing a staff of 10 persons, coordinate the activities of the shop and the restaurant, budgeting and cost controls, inventory management, scheduling staff hours and ordering supplies, staff recruitment, ensure service satisfaction to customers, strong knowledge of Health \& Safety rules and regulations, train new employees, high availability and flexibility.
  }{%
    {\bf Manager Adjoint,}
    Delitraiteur France, Bourg la Reine, France.
    {\it Véritable manager en son absence,}
    {\it Responsable d'équipe: Gestion des commandes et du stock. Supérvision des tâches des employés. Gestion des conflits humain et technique. Recrutement. Responsable ouverture et fermeture magasin.}
    {\it Responsable HACCP: Mise en place de procédures d'hygiène et contrôle du respect des règles.}
    Manager une équipe. Gérer un service. Gestion administrative du restaurant. Polyvalence.
  }{%
    {\ bfAssistant  Manager}
    Delitraiteur France, Bourg la reine, Frankreich.
 
    {\it Assistant Manager in einem luxuriösen Geschäft mit Restaurant- und Cateringbereich.}
 
    {\bf Kompetenzen :} Führung einer Mannschaft von 10 Personen, Koordinierung der Aktivitäten des Geschäfts und des Restaurants, Budget-  und Kostenkontrolle, Inventarmanagement, Programmierung des Stundenplans der Mitarbeiter und Bestellung der  Vorräte, Personnaleinstellung, Qualitätsservicekontrolle /  Klientenzufriedenheit, bestes Wissen der Vorschriften und Bestimmungen im  Gesundheits- / Sicherheitsbereich, Schulung neuer Mitarbeiter, hohe  Disponibilität und Flexibilität.
  }

% 2008
\item[2008]
  \lang{%
    {\bf Internship in the Food and Beverage department,} 4 months, 
    Hilton, Strasbourg, France.

    {\it Head waiter in the gourmet restaurant and head chef assistant in the kitchen of a famous chain hotel. }%
  }{%
    {\bf Stage en restauration} 4 mois
    Hilton, Strasbourg, FRANCE.
    {\it Chef de rang: Prise de commandes, gestion des plaintes, formation du personnel, service banquet.}
    {\it Cuisine, sous-chef de partie: Travail en coopération avec le Chef de partie sur les hors-d'oeuvre, pâtisserie et traiteur. Relations fournisseurs.}
  }{%
    {\bf Stage in der Restauration} 4 Monate
    Hilton, Strasbourg, Frankreich.
     
    {\it Oberkellnerin / chef de rang im Gourmet Restaurant und Assistentin des Küchenchefs  / sous-chef de partie einer international renommierten Hotelkette.}

  }

% 2007-2008
\item[2007-2008]
  \lang{%
    {\bf Head waiter, part-time contract}
    Restaurant de La Bourse, Strasbourg, France.

    {\it Head waiter in a luxurious gourmet restaurant. }%
  }{%
    {\bf Chef de rang, contrat à mi-temps,}
    Restaurant de La Bourse, Strasbourg, FRANCE.
    Chef de rang dans un restaurant brasserie de luxe. Prise de commandes, Emission de factures, service banquet, utilisation d'un système d'enregistrement des commandes.
  }{%
    {\bf Oberkellnerin / chef de rang, Teilzeitvertrag}
    Restaurant de la Bourse, Strasbourg, Frankreich
  
    {\it Oberkellnerin / chef de rang im Restaurant /  Brasserie de luxe. Aufnahme der Bestellungen, Ausstellung der Rechnungen, Banketservice, Benutzung/Handhabung eines Registriegunssystem des Bestellungen.}
  }

% 2007
\item[2007]
  \lang{%
    {\bf Internship in the hotel industry,} 4 months,
    Hôtel Le Yaca****, Saint-Tropez, France.
    
    {\it Hotel receptionnist and head waiter in the restaurant of 4-star hotel located in a world-known location.}%
  }{%
    {\bf Stage en restauration} 4 mois
    Hôtel Le Yaca****, Saint-Tropez, France.
    {\it Réception: Prise de réservations, traitement des factures et de la caisse, gestion arrivées-départs, contacts avec des agences de voyages, formation de personnel.}

    {\it Chef de rang: Service du petit déjeuner et du soir. Prise de commandes, traitement des plaintes et service à l'assiette.}
    {\it Service des étages: Service de couverture en autonomie.}
  }{%
    {\bf Stage im Hotelbereich} 4 Monate
    Hotel Le Yaca****, Saint-Tropez, Frankreich.

    {\it Hotel Rezeptionist und Oberkellnerin / chef de rang im Restaurant eines 4 Sterne Hotel in einem weltweiten und reputierten Ort}
  }

\end{CV}

% Education
\section{\lang{Education}{Formation universitaire}{Ausbildung}}
\begin{CV}[2]{-4.5ex}
\smallskip

\item[2006-2009]
  \lang{%
    {\bf Higher national degree, hotel management and marketing} Lycée Alexandre Dumas, Strasbourg, France.
    {\it Financial management. Commercial and marketing strategies.}
  }{%
    {\bf BTS en hôtellerie restauration, gestion hôtelière} Lycée Alexandre Dumas, Strasbourg.%
  }{%
    {\bf Hoherer Abschluss im Hotelmanagement und marketing} Lycée Alexandre Dumas, Strasbourg, Frankreich.
    {\it Finanzmanagement, Handels- und Marketingstrategien}
  }

\item[2004-2006]
  \lang{%
    {\bf Baccalaureat exam with a specialization in Economics and Social Studies} Lycée Français de Berlin, Berlin, Germany.%
    {\it Social sciences, philosophy, management, business administration, economics, mathematics and history.}
  }{%
    {\bf Baccalauréat, Économique et Social,} Lycée Français de Berlin, Berlin, Allemagne.
  }{%
    {\bf Abitur  mit Spezialisierung auf Economics und Social Studies} Lycée Français de Berlin, Berlin, Germany
   {\it Social sciences, philosophy, management, business administration, economics, mathematics and history}
  }

\end{CV}

\section{\lang{Interests}{Centres d'intérêts}{Interressenschwerpunkt}}
\begin{CV}[2]{-4.5ex}
  \smallskip
  \smallskip
  
\item
{\bf \lang{Countries lived in}{Les pays habités}{Aufenthalt in verschiedenen Ländern}:}
\lang{Bonn, Germany}{Bonn, Allemagne}{Bonn, Deutschland} (1987-1990),
\lang{Rabat, Morocco}{Rabat, Maroc}{Rabat, Marocco} (1990-1997),
\lang{Singapore}{Singapour}{Singapour} (1997-1998),
\lang{Cairo, Egypt}{Le Caire, Egypte}{Cairo, Ägypten} (1998-2001),
\lang{Vienna, Austria}{Vienne, Autriche}{Wien, Österreich} (2001-2002),
\lang{Warsaw, Poland}{Varsovie, Pologne}{Warschaw, Poland} (2002-2004),
\lang{Berlin, Germany}{Berlin, Allemagne}{Berlin, Deutschland} (2004-2006),
\lang{Strasbourg, France}{Strasbourg, France}{Strasbourg, Frankreich} (2006-2008),
\lang{Cairo, Egypt}{Le Caire, Egypte}{Cairo, Ägypten} (2008-2009).
\lang{Paris and Angers, France}{Paris et Angers, France}{Paris und Angers, Frankreich} (2009-current).

  %\smallskip
  
  \lang{
  \item \textbf{Sports:} Cycling, climbing and dancing.
  \item \textbf{Hobbies:} Animal welfare, foreign cultures and languages, travelling, cinema, music
  }{%
  \item \textbf{Sports:} équitation, vélo et danse.
  \item \textbf{Loisirs:} histoire, cultures et langues étrangères, voyages, cinéma, musique et lecture
  }{%
  \item \textbf{Sports:} Radfahren, Klettern und Tanzen.
  \item \textbf{Freizeitaktivitäten:} Tierschutz, fremde Sprachen und Kulturen, Reisen, Cinema und Musik
  }
\end{CV}

\end{document}
